Multiple regression: TRELIS-Q WP5 data

### 2024-05-27 Rmd/bookchapter.TRELIS-Q-WP5.Rmd
Added NFSUN-plot

@@

>>>>

Changelog:

* 16.5.2024: added plot for NFSUN2024

@@

For NFSUN2024:

```{r}
stolpediagram <- ggplot(dc, aes(x=studiested2, y=var, fill=studiested2)) + 
  geom_bar(stat="identity", position="dodge") +
  #scale_fill_manual(values=viridis(3)) + 
  geom_errorbar(aes(ymin=var-sd, ymax=var+sd), # se
                  linewidth=.3,    # Thinner lines
                  width=.2,
                  position=position_dodge(.9)) +
  ggtitle("Mean PCK, TK and TPACK for science teacher institutes") +
  guides(fill="none") +
  # https://stackoverflow.com/questions/53843221/make-y-axis-start-at-1-instead-of-0-within-ggplot-bar-chart
#  coord_cartesian(ylim = c(1,5)) +
  ylab("Value") +
  xlab("Institute group") +
  theme_bw() +
  facet_wrap(~TPACK)
